---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```
 
```{css}
@import url('https://fonts.googleapis.com/css2?family=Big+Shoulders+Inline&family=Roboto+Condensed&display=swap');

h2{
color:red;
font-family: "Big Shoulders Inline", serif;
font-weight: 800;
font-style: italic;
 
}

body{
font-family: "Roboto Condensed", serif;
font-weight: 700;
font-style: normal;
}

```

## Introduction

This report analyzes observational data collected on public transport use. Data is collected through Google Forms surveys and stored in Google Forms. The goal is to investigate data such as the time taken by passengers, the number of passengers, comfort and bus occupancy.

```{r}
library(tidyverse)
logged_data = read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTUV2Zh8ODNKQVXaxTVKh35PTMexvnA7ocRS8FFg_xCbRyEbtaEuR-7zewIq6x0JoCoIGVMpfrKxPHP/pub?gid=618838588&single=true&output=csv")
```

## data frame
```{r}
## data prepare

latest_data = logged_data %>% 
  rename(Date=2,Time=3,Passengers=4,P_action =5,bus_full_Status =6,comfort_rate=7)

latest_data  = latest_data[ ,-1] #Remove the first column (unwanted data)
latest_data

```

 
## Summary values
```{r}

summary_values <- latest_data %>%
  summarise(
    # Calculate the mean number of passengers, and mean environment score
    Avg_Passenger_Count = round(mean(Passengers, na.rm = TRUE),0),
    max_passenger = max(Passengers, na.rm = TRUE),
    max_passenger_time =format(Time[which.max(Passengers)]),
    Avg_Environment_Rating = round(mean(comfort_rate, na.rm = TRUE),2),
    most_feedback = names(table(comfort_rate)[which.max(table(comfort_rate))])
  )

```
```{r}
paste0("From our summary of the survey we know the average passengers number is",summary_values["Avg_Passenger_Count"],"and the overall feedback score of the comfort is",summary_values["Avg_Environment_Rating"])
```
## passengers number count in different time

```{r}
latest_data %>% 
  ggplot() +
   geom_bar(aes(x = Time),fill = "red") +
  labs(title = "Passenger Count by Time Period", 
       x = "Time", 
       y = "Passengers") +
  theme_minimal()
```

```{r}
paste("In this bar chart we can see the max number of passengers is ",summary_values["max_passenger"],"at",summary_values["max_passenger_time"] )
```


## bus_full_Status & comfort_rate
```{r}
latest_data %>% 
  ggplot() +
  geom_bar(aes(x = comfort_rate),fill = "blue") +
  labs(title = "What is the full status of the bus for passengers' comfort", 
       x = "comfort_rate", 
       y = "bus_full_Status") +
  theme_minimal()

```

```{r}
paste("In this table, we can see the most comfort rate is",summary_values["most_feedback"])
```







